---
output:
  html_document:
    bibliography: bibtex
    highlight: tango
    keep_md: yes
    theme: spacelab
---

### Last Update

```{r}
Sys.time()
```


### Data Set

The data sets have been directly retrived with an own Facebook application.

From each of following Facebook pages the last 500 posts have been imported.

Related pages:

* [Douglas][1]

* [Flaconi][2] 

* [Pieper][3] 
        
* [Parfurmdreams][4] 

* [iparfumerie][5] 

***

### Notices

This application is primarily a demo to show what is possible. 

In case of any questions related to this application, feel free to write [me a mail.][6]

***

### Used R Packages

```{r, eval=FALSE}
library(graph)
library(Rfacebook)
library(NLP)
library(tm)
library(shinyIncubator)
library(grid)
library(pvclust)
library(Rgraphviz)
library(qdapTools)
library(qdapRegex)
library(magrittr)
library(wordcloud)
library(RColorBrewer)
library(ggplot2)
library(rJava)
library(RCurl)
library(bitops)
library(BH)
library(ape)
library(topicmodels)       
library(qdap)
library(shinythemes)
```

***

### Last Session Info

```{r}
devtools::session_info()
```



[1]: https://www.facebook.com/DouglasDeutschland "Douglas Deutschland"

[2]: https://www.facebook.com/flaconi.de "Flaconi"

[3]: https://www.facebook.com/Parfuemerie.Pieper "Stadt-Parfümerie Pieper"

[4]: https://www.facebook.com/parfumdreams "Parfumdreams"

[5]: https://www.facebook.com/iparfumerie.de "iparfumerie.de"

[6]: http://nierhoff.info/#contact "Contact"

***
