---
output:
  html_document:
    bibliography: bibtex
    highlight: null
    keep_md: yes
    theme: null
---

### Last Update

```{r}
Sys.time()
```

***

### Code

The code of this application can be found in this [Github repository][1].

### Data Set

```{r, echo=FALSE}
uni <- read.csv(file = "./data/Unitymedia.csv", sep=",", header = TRUE)
vod <- read.csv(file = "./data/Vodafone.csv", sep=",", header = TRUE)
tel <- read.csv(file = "./data/Telekom.csv", sep=",", header = TRUE)
eins <- read.csv(file = "./data/einsundeins.csv", sep=",", header = TRUE)
```


The data sets have been directly retrived with an own Twitter application.

Related Twitter Accounts:

* [Unitymedia][2]

        Number of analyzed tweets after cleaning: `r length(uni[,1])`

* [Telekom][3] 

        Number of analyzed tweets after cleaning: `r length(tel[,1])`

* [Vodafone][4] 
        
        Number of analyzed tweets after cleaning: `r length(vod[,1])`
        
* [1&1][5] 
        
        Number of analyzed tweets after cleaning: `r length(eins[,1])`

***

### Notices

This application is primarily a demo to show what is possible. 

In case of any questions related to this application, feel free to write [me a mail.][6]

***

### Used R Packages

```{r, eval=FALSE}
library(graph)
library(twitteR)
library(NLP)
library(tm)
library(shinyIncubator)
library(grid)
library(pvclust)
library(Rgraphviz)
library(qdapTools)
library(qdapRegex)
library(magrittr)
library(wordcloud)
library(RColorBUnitymediar)
library(ggplot2)
library(RCurl)
library(bitops)
library(shinyapps)
library(BH)
library(qdap)
library(SnowballC)
library(slam)
library(RWeka)
library(rJava) 
library(RWekajars)
library(memoise)
library(devtools)
library(rjson)
library(bit64)
library(httr)
library(plyr)
library(dendextend)
library(rJava)
library(topicmodels)
library(shinythemes)
```

***

### Last Session Info

```{r}
devtools::session_info()
```



[1]: https://github.com/mhnierhoff/shiny-apps/tree/master/unitymedia "Github Repo"

[2]: https://twitter.com/unitymedia "Unitymedia Twitter Account"

[3]: https://twitter.com/deutschetelekom "Telekom Twitter Account"

[4]: https://twitter.com/vodafone "Vodafone Twitter Account"

[5]: https://twitter.com/1und1 "1&1 Twitter Account"

[6]: http://nierhoff.info/#contact "Contact"

***
