---
output:
  html_document:
    bibliography: bibtex
    highlight: null
    keep_md: yes
    theme: null
---

### Last Update

```{r}
Sys.time()
```

***

### Code

The code of this application can be found in this [Github repository][1].

### Data Set

```{r, echo=FALSE}
a <- read.csv(file = "./data/REWE.csv", sep=",", header = TRUE)
r <- read.csv(file = "./data/toom.csv", sep=",", header = TRUE)
p <- read.csv(file = "./data/BIPA.csv", sep=",", header = TRUE)
```


The data sets have been directly retrived with an own Twitter application.

Related Twitter Accounts:

* [REWE][2]

        Number of analyzed tweets after cleaning: `r length(a[,1])`

* [toom][3] 

        Number of analyzed tweets after cleaning: `r length(r[,1])`

* [BIPA][4] 
        
        Number of analyzed tweets after cleaning: `r length(p[,1])`

***

### Notices

This application is primarily a demo to show what is possible. 

In case of any questions related to this application, feel free to write [me a mail.][5]

***

### Used R Packages

```{r, eval=FALSE}
library(graph)
library(twitteR)
library(NLP)
library(tm)
library(shinyIncubator)
library(grid)
library(pvclust)
library(Rgraphviz)
library(qdapTools)
library(qdapRegex)
library(magrittr)
library(wordcloud)
library(RColorBrewer)
library(ggplot2)
library(RCurl)
library(bitops)
library(shinyapps)
library(BH)
library(qdap)
library(SnowballC)
library(slam)
library(RWeka)
library(rJava) 
library(RWekajars)
library(memoise)
library(devtools)
library(rjson)
library(bit64)
library(httr)
library(plyr)
library(dendextend)
library(rJava)
library(topicmodels)
library(shinythemes)
```

***

### Last Session Info

```{r}
devtools::session_info()
```



[1]: https://github.com/mhnierhoff/shiny-apps/tree/master/rewetm "Github Repo"

[2]: https://twitter.com/rewe_supermarkt "REWE Twitter Account"

[3]: https://twitter.com/toomteam "toom team Twitter Account"

[4]: https://twitter.com/BIPA "BIPA Twitter Account"

[5]: http://nierhoff.info/#contact "Contact"

***
