---
output:
  html_document:
    highlight: tango
    keep_md: yes
    theme: spacelab
---

### Last Update

```{r}
Sys.time()
```

***

### Data Set

The used data set was derived from an own account and own comparisons by the use of Alexa.com Competitive Intelligence metrics.

The presented forecasts relate to the Alexa Time on Site metric.

***

### Forecasting Models

#### Auto.Arima
Fit best ARIMA model to univariate time series

**Description**

Returns best ARIMA model according to either AIC, AICc or BIC value. The function conducts a search over possible model within the order constraints provided.

***

#### ETS
Exponential smoothing state space model

**Description**

Returns ets model applied to y.

***

#### TBATS
TBATS model (Exponential smoothing state space model with Box-Cox transformation, ARMA errors, Trend and Seasonal components)

**Description**

Fits a TBATS model applied to y, as described in De Livera, Hyndman & Snyder (2011). Parallel processing is used by default to speed up the computations.

***

#### StructTS
Forecasting using Structural Time Series models

**Description**


Returns forecasts and other information for univariate structural time series models.

***

#### Holt-Winters
Forecasting using Holt-Winters objects

**Description**

Returns forecasts and other information for univariate Holt-Winters time series models.

***

#### Theta
Theta method forecast

**Description**

Returns forecasts and prediction intervals for a theta method forecast.

***

#### Random Walk
Random Walk Forecast

**Description**

Returns forecasts and prediction intervals for a random walk with drift model applied to x.

***

#### Naive
Naive forecasts

**Description**

```naive()``` returns forecasts and prediction intervals for an ARIMA(0,1,0) random walk model ap- plied to x. ```snaive()``` returns forecasts and prediction intervals from an ARIMA(0,0,0)(0,1,0)m model where m is the seasonal period.

***

#### Cubic Spline
Cubic Spline Forecast

**Description**

Returns local linear forecasts and prediction intervals using cubic smoothing splines.

***

#### Mean
Mean Forecast

**Description**

Returns forecasts and prediction intervals for an iid model applied to x. 

***

### Notices

This application is primarily a demo to show what is possible. In favor of the ease of use of this app, the individual models may not be maximally accurate.

In case of any questions related to this application, feel free to write [me a mail.][1]

***

### Used R Packages

```{r, eval=FALSE}
library(shiny)
library(shinyIncubator)
library(zoo)
library(timeDate)
library(datasets)
library(forecast)
library(knitr)
library(rmarkdown)
library(lubridate)
```

***

### Last Session Info

```{r}
Sys.time()
sessionInfo()
```

***

### References

Hyndman RJ (2015). forecast: Forecasting functions for time series and linear models. R package version 5.8, http://github.com/robjhyndman/forecast.

Hyndman RJ and Khandakar Y (2008). “Automatic time series forecasting: the forecast package for R.” Journal of Statistical Software, 26(3), pp. 1–22. http://ideas.repec.org/a/jss/jstsof/27i03.html.

[1]: http://nierhoff.info/#contact "Contact"

***
