---
output:
  html_document:
    bibliography: bibtex
    highlight: tango
    keep_md: yes
    theme: spacelab
---

### Last Update

```{r}
Sys.time()
```

***

### Code

The code of this application can be found in this [Github repository.][1]

***

### Data Set

The used data set was derived from an own account and own comparisons by the use of Alexa.com Competitive Intelligence metrics.

About the metric:

> Time on Site: The estimated daily time on site in seconds for this site. Historical data not available for sites ranked > 100,000

The presented plots, forecasts and calculations relate to the Alexa Time on Site metric.

Related websites:

* [navabi][2]

* [sheego][3]

* [happy-size][4]

* [ullapopken][5]


***

### Notices

This application is primarily a demo to show what is possible. 

In case of any questions related to this application, feel free to write [me a mail.][6]

***

### First Tab - Overview

In simple but appropriate words:

> In statistics, exploratory data analysis (EDA) is an approach to analyzing data sets to summarize their main characteristics, often with visual methods. [(wikipedia.org)][7]

The line chart gives an first impression of the selected data set, while the boxplot shows the median, quartiles, outliers and also gives a first view on the respective distribution. The summary lists all relevant results for a discriptive statistical analysis. Finally the histogram enables a clear presentation of the distribution of the selected data set. At least the raw data tab makes it possible to check every single value of the data set.

***

### Second Tab - Forecasting Models

#### Auto.Arima
Fit best ARIMA model to univariate time series

**Description:**

Returns best ARIMA model according to either AIC, AICc or BIC value. The function conducts a search over possible model within the order constraints provided.

***

#### ETS
Exponential smoothing state space model

**Description:**

Returns ets model applied to y.

***

#### TBATS
TBATS model (Exponential smoothing state space model with Box-Cox transformation, ARMA errors, Trend and Seasonal components)

**Description:**

Fits a TBATS model applied to y, as described in De Livera, Hyndman & Snyder (2011). Parallel processing is used by default to speed up the computations.

***

#### StructTS
Forecasting using Structural Time Series models

**Description:**


Returns forecasts and other information for univariate structural time series models.

***

#### Holt-Winters
Forecasting using Holt-Winters objects

**Description:**

Returns forecasts and other information for univariate Holt-Winters time series models.

***

#### Theta
Theta method forecast

**Description:**

Returns forecasts and prediction intervals for a theta method forecast.

***

#### Random Walk
Random Walk Forecast

**Description:**

Returns forecasts and prediction intervals for a random walk with drift model applied to x.

***

#### Naive
Naive forecasts

**Description:**

```naive()``` returns forecasts and prediction intervals for an ARIMA(0,1,0) random walk model ap- plied to x. ```snaive()``` returns forecasts and prediction intervals from an ARIMA(0,0,0)(0,1,0)m model where m is the seasonal period.

***

#### Cubic Spline
Cubic Spline Forecast

**Description:**

Returns local linear forecasts and prediction intervals using cubic smoothing splines.

***

#### Mean
Mean Forecast

**Description:**

Returns forecasts and prediction intervals for an iid model applied to x. 

***

#### References for the Forecast R package

Hyndman RJ (2015). forecast: Forecasting functions for time series and linear models. R package version 5.8, http://github.com/robjhyndman/forecast.

Hyndman RJ and Khandakar Y (2008). “Automatic time series forecasting: the forecast package for R.” Journal of Statistical Software, 26(3), pp. 1–22. http://ideas.repec.org/a/jss/jstsof/27i03.html.

***

### Third Tab - Breakout Detection

The Breakout Detection is being solved through the Twitter R package with the respective name. You can check the code and more information in their [repo on Github.][8]

> The underlying algorithm – referred to as E-Divisive with Medians (EDM) – employs energy statistics to detect divergence in mean. Note that EDM can also be used detect change in distribution in a given time series. EDM uses robust statistical metrics, viz., median, and estimates the statistical significance of a breakout through a permutation test.

***

### Fourth Tab - Decomposition

#### Normal Timeseries Decomposition

This decomposition formula splits the data into seasonal, trend and irregular components using moving averages. The additive model uses the following formula: Y[t] = T[t] + S[t] + e[t].

#### STL Decomposition

> STL is a very versatile and robust method for decomposing time series. STL is an acronym for “Seasonal and Trend decomposition using Loess”, while Loess is a method for estimating nonlinear relationships. The STL method was developed by Cleveland et al. (1990) [(Source)][9]

***

### Fifth Tab - Calendar View

The view of the data in a calendar allows to inspect the respective values per day interactively and also enables a quick detection of differences between weekdays and weekends. Furthermore, seasonal differences can also be discovered at a first glance.

***

### Used R Packages

```{r, eval=FALSE}
library(zoo)
library(timeDate)
library(forecast)
library(lubridate)
library(shiny)
library(shinyIncubator)
library(shinythemes)
library(knitr)
library(reshape)
library(DT)
library(RColorBrewer)
library(googleVis)
library(BreakoutDetection)
library(rmarkdown)
```

***

### Last Session Info

```{r}
sessionInfo()
```


[1]: https://github.com/mhnierhoff/shiny-apps/tree/master/navabi "Github Repo"

[2]: http://www.navabi.de "navabi Website"

[3]: http://www.sheego.de "sheego Website"

[4]: http://www.happy-size.de "happy-size Website"

[5]: http://www.ullapopken.com "ullapopken Website"

[6]: http://nierhoff.info/#contact "Contact"

[7]: http://en.wikipedia.org/wiki/Exploratory_data_analysis "EDA on wikipeda.org"

[8]: https://github.com/twitter/BreakoutDetection "Twitter Breakout Detection R Package"

[9]: https://www.otexts.org/fpp/6/5 "STL Decomposition"

***
